Radio Emission from Red-Giant Hot Jupiters

### 2015-09-28 ms.tex
description about the comparison with Ignace (2010) is revised

Equation (\ref{eq:F_nu_RGHJ}) gives the value which is by factor smaller than the prediction of equation (5) in \citet{ignace2010} in the case of $\eta = 1$. This originates from the different scaling laws for the planetary magnetic field and that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind.

>>>>

Equation (\ref{eq:F_nu_RGHJ}) gives the value which is orders of magnitude smaller than the prediction of equation (5) in \citet{ignace2010} if we assume the same set of fiducial parameters and full ionization. This mainly originates from that their formulation didn't incorporate the effect of compressed planetary magnetosphere due to massive stellar wind, while the scaling law for the planetary magnetic field strength is also different.
